\section{Interplay of quark and lepton flavour}

As previously highlighted, many of the observables whose experimental
measurements reveal lingering tensions with respect to the SM
theoretical expectations consist of a large variety of 
(very) rare processes, among them semi-leptonic
or leptonic meson decays.

Particularly interesting examples of
these are the semi-leptonic and leptonic $R_K$ ratios, 
$R_K = \cb(B\to K\mu\mu)/\cb(B\to Kee)_{{\rm low}-q^2}$ (exhibiting a 
$2.6\sigma$ deviation from its SM prediction), and 
$R_K^{\rm leptonic} = \cb(K\to \mu\mu)/\cb(K\to ee)$.
Both the latter observables could signal the violation of lepton flavour
universality, which might possibly be a consequence of charged lepton
flavour violation\footnote{For recent studies on $R_K^{\rm leptonic}$, see for
  example~\cite{Fonseca:2012kr,Abada:2012mc,Abada:2013aba}.}.   
 
Understanding these tensions (if confirmed) calls for extensions of the SM, 
leading to modifications of its flavour paradigm. While many New Physics
constructions address the hadronic sector, others aim at explaining 
the experimental tensions
from the leptonic point view. 
By itself, flavour violation in the charged lepton sector is an 
unambiguous signal of New Physics. The experimental effort
devoted to search for cLFV in a variety of processes 
(MEG, Mu2e, Mu3e, COMET, LHCb, SuperB, future FCC-ee and LC, ...)
implies that in the near future the 
different bounds will become much stronger, further lending hope to a
possible observation. 

From a theoretical point of view, it is also important to stress that
certain well-motivated constructions called upon to address the quark flavour
puzzle have unavoidable implications regarding lepton flavours as
well. 
Examples of such constructions include extended Higgs sectors
(several realisations of 2HDM, type II seesaw, ...),
extended gauge sectors 
(e.g., additional $Z^\prime$ bosons) or additional symmetries - flavour
symmetries, or gauge ones, such as left-right symmetric models -, and finally 
larger frameworks as general Supersymmetry, extra dimensional models and
Grand Unified Theories. 

In all cases, it is clear that one must 
carefully evaluate the possible contributions to the
distinct charged lepton flavour observables: these include 
purely leptonic processes, such as 
radiative $\ell_i \to \ell_j \gamma$, 3-body $\ell_i \to 3\ell_j$,
etc., or processes involving hadron as is the case of semileptonic 
tau decays (such as $\tau \to \ell_i$+light hadrons), leptonic and 
semileptonic $B$, $D$
and $K$ meson decays, ..., and finally Higgs and $Z$ flavour violating
decays.
The expected contributions must be 
confronted with the available (and soon to
be improved) bounds, which will further allow one to constrain the
parameter space of different theoretical models, possibly
impacting on the associated predictions regarding flavour
violation in the hadron sector. 
The synergy between the observables might allow to 
readily exclude some of these well-motivated scenarios, and 
possibly to discriminate among distinct realisations of 
flavour violating models 
(see, e.g.,~\cite{Abada:2014cca,Abada:2015zea,Abada:2015oba}). 

\medskip
It is important to stress that the
studies referred to above 
will clearly also have an impact on other flavour conserving 
observables, as is the case for the muon anomalous magnetic moment
$(g-2)_\mu$ 
or electric dipole moments of leptons. The exploration of these observables
(already foreseen in the present Scientific Proposal) might offer 
additional insight into the lepton and quark flavour puzzle.


\medskip
Considering the interplay between quark and lepton flavour
violation, combining the informations and data arising from each
sector, is thus relevant (and even mandatory!) to fully understand 
the underlying theory of flavour, and constrain - or even identify -
the New Physics model at its origin. 


%% %%%%%%%%%%%%%%%%%%%%%%

%% \bibitem{Fonseca:2012kr}
%%   R.~M.~Fonseca, J.~C.~Romao and A.~M.~Teixeira,
%%   %``Revisiting the $\Gamma(K \to e \nu)/\Gamma(K \to \mu \nu)$ Ratio in Supersymmetric Unified Models,''
%%   Eur.\ Phys.\ J.\ C {\bf 72} (2012) 2228
%% %  doi:10.1140/epjc/s10052-012-2228-2
%%   [arXiv:1205.1411 [hep-ph]].

%% \bibitem{Abada:2012mc}
%%   A.~Abada, D.~Das, A.~M.~Teixeira, A.~Vicente and C.~Weiland,
%%   %``Tree-level lepton universality violation in the presence of sterile neutrinos: impact for $R_K$ and $R_\pi$,''
%%   JHEP {\bf 1302} (2013) 048
%% %  doi:10.1007/JHEP02(2013)048
%%   [arXiv:1211.3052 [hep-ph]].

%% \bibitem{Abada:2013aba}
%%   A.~Abada, A.~M.~Teixeira, A.~Vicente and C.~Weiland,
%%   %``Sterile neutrinos in leptonic and semileptonic decays,''
%%   JHEP {\bf 1402} (2014) 091
%% %  doi:10.1007/JHEP02(2014)091
%%   [arXiv:1311.2830 [hep-ph]].

%% \bibitem{Abada:2014cca}
%%   A.~Abada, V.~De Romeri, S.~Monteil, J.~Orloff and A.~M.~Teixeira,
%%   %``Indirect searches for sterile neutrinos at a high-luminosity Z-factory,''
%%   JHEP {\bf 1504} (2015) 051
%% %  doi:10.1007/JHEP04(2015)051
%%   [arXiv:1412.6322 [hep-ph]].

%% \bibitem{Abada:2015zea}
%%   A.~Abada, D.~Becirevic, M.~Lucente and O.~Sumensari,
%%   %``Lepton flavor violating decays of vector quarkonia and of the $Z$ boson,''
%%   Phys.\ Rev.\ D {\bf 91} (2015) no.11,  113013
%% %  doi:10.1103/PhysRevD.91.113013
%%   [arXiv:1503.04159 [hep-ph]].

%% \bibitem{Abada:2015oba}
%%   A.~Abada, V.~De Romeri and A.~M.~Teixeira,
%%   %``Impact of sterile neutrinos on nuclear-assisted cLFV processes,''
%%   JHEP {\bf 1602} (2016) 083
%% %  doi:10.1007/JHEP02(2016)083
%%   [arXiv:1510.06657 [hep-ph]].
